% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Michael Stanton}}

Wallbergstrasse 28\ \ \textbullet
\ \ Markt Schwaben, Germany 85770
\\
+49 (0) 151 4454 3634\ \ \textbullet
\ \ ripsawridge@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Google Corporation}}
		{\textbf{Munich, Germany}}
	\\
	\headerrow
		{\emph{Senior Software Engineer}}
		{\emph{2012 -- 2021}}
	\begin{itemize*}
    \item V8 is the JavaScript compiler and runtime environment shipped in Google
Chrome and Node.js, providing optimized code execution to over a billion
users.
    \item Led a team of senior developers to produce the TurboFan optimizing JavaScript
compiler, shipping in V8 since 2017.
    \item Led the effort to make TurboFan fully concurrent, a challenging project because the
compiler must introspect into continually mutating data structures to achieve high
performance. Success required the creation of new
heuristics, programming idioms, and testing modes that utilize TSAN (Thread Sanitizer).
Shipping in Chrome since November, 2021.
    \item Adapted V8 to support the Intel CET Shadow Stack, new hardware meant to
prevent ROP attacks.
    \item Developed the Feedback Vector to collect runtime feedback in JavaScript
programs. This enabled adding an interpreter to V8 in 2015.
    \item I hold a patent for AllocationSites, a method for choosing ideal representation
of arrays, and serving as a pretenuring platform for generational garbage
collectors.
    \item Spoke often to university students about working in V8, at Google, and in the
software industry in general from my experience as an individual contributor
and manager. Wrote blog articles to explain arcane subjects to coding
enthusiasts.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Advanced Medical Diagnostics}}
		{\textbf{Waterloo, Belgium}}
	\\
	\headerrow
		{\emph{Software Engineer Lead}}
		{\emph{2009 -- 2012}}
	\begin{itemize*}
    \item Development team Lead for the HistoScanning product, which detects regions
of interest in a reconstructed, segmented prostate gland from ultrasound data.
    \item Implemented a re-write of the visualization system using the open
source VTK library. 
    \item Responsibilities included UI development with WPF,
database design and implementation (NHibernate, Spring.NET), detecting and
solving performance issues, servo-motor control, and interface API design for a
custom-built ultrasound machine. Development of a custom plugin solution to
package and ship sensitive or updatable components. Interface with research
team for special visualizations and data import/export from MATLAB.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Avid Corporation}}
		{\textbf{Munich, Germany}}
	\\
	\headerrow
		{\emph{Principal Software Engineer}}
		{\emph{2005 -- 2009}}
	\begin{itemize*}
    \item Worked in a principal design role for the next-gen
  Interplay Server, which is a redesign of the previous C++ system using
  Java, Spring, Hibernate and SQL. Cross-team coordination between
  engineering teams in Munich, Tewksbury and Montreal. Employment of
  Agile development processes (SCRUM, sprints). Debugging and feature
  implementation in the legacy C++ server as well.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Microsoft Corporation}}
		{\textbf{Redmond, Washington, USA}}
	\\
	\headerrow
		{\emph{Software Engineer/Lead}}
		{\emph{1998 -- 2005}}
	\begin{itemize*}
    \item Led a team of 4 focused on fixing race 
    conditions, leaks and crashes in the Common Language Runtime (CLR) 
    version 2.0. Responsibilities include debugging/fixing hard-to-reproduce 
    issues, being the primary development contact for Product Support in the 
    field with Customer stress issues, and improving the product with smarter 
    coding practices and test runs.
    
    \item Contributed to design and implementation of managed breakpoint support in 
    unmanaged debuggers. Exceptions can optionally be raised by the CLR when 
    methods are just-in-time compiled, then handled by the debugger which 
    then has an address to set breakpoints.

    \item Adding and maintaining features of the SOS.DLL CLR debugging tool. Maintain 
    a blog and give presentations on the tool, geared towards debugging CLR 
    issues on servers or from dump files.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Intel Corporation}}
		{\textbf{Portland, Oregon, USA}}
	\\
	\headerrow
		{\emph{Software Engineer}}
		{\emph{1996 -- 1998}}
	\begin{itemize*}
    \item Implemented the on-line update feature of an online 
    help and antivirus system. Network detection and download 
    of patches, restart after patch application, etc.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{University of Texas}}
		{\textbf{Austin, Texas}}
	\\
	\headerrow
		{\emph{B.S. Computer Science}}
		{\emph{1993 -- 1996}}
	\begin{itemize*}
    \item 3.9 GPA in major Concentration
    \item Working knowledge of German, written and spoken
    \item Authored a tutorial on implementing structured data types in
  Mathematica for the book "Abstract Data Types," by Dr. Nell Dale.
	\end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	C, \CPP, JavaScript, Python, Java, x86/x64 assembly, shell script, SQL
	\item[Technologies:]
	Linux, Docker containers, Subversion, Git,
   Spring, Hibernate, WPF
\end{description*}
\end{indentsection}

\end{document}
